On the discovery and origin of $r$-process stars in the Milky Way

### 2018-04-13 article/ms.tex
updated things and all that

	In order to answer these questions it is necessary to identify a large sample of r-process stars.
	However, r-process stars are very rare. For this reason we must look to massive data sets, such as the LAMOST sky survey. In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 26 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017,Sakari2018}.
	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods. In Section 3 we discuss what our results imply about the sites of the r-process. We provide concluding remarks in Section 4.

@@

	\subsection{Neutron-star mergers}
	\label{NSmerg}
	Neutron-star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}. They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur. This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}, consistent with observed ejecta \citep{Kasliwal2017}. However, the direct interaction and merger of a binary neutron-star pair occurs very infrequently, with currently only one direct observation, and with a most plausible frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016,Abadie2010} well within the the outer estimates of $320 and 4780\ \rm{Gpc^{-3}yr^{-1}}$. The significant amount of material that these mergers release can compensate for their low frequency and so it could be that they are responsible for most if not all r-process enhancements observed.

@@

    It was found that in the Milky Way there should be present 13,060 r-process stars enhanced solely from neutron-star mergers. Taking into account that this should be considered a upper-bound estimate this is still a startlingly large difference from the known 73 r-process stars in the Milky Way.

    In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3 stars per year. Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$. This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents. Multiplying this fraction by the 13,060 stars that should be present in the Milky Way, we expect to be present 79 enhanced stars in LAMOST DR2, a number consistent with the 73 we now know of.

@@

    Following from the assumptions listed and calculations above, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.9\times10^{9}$ years, very close to the age of the universe. From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe. This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, that core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.

@@

@@

	% Don't change these lines
	%\bsp	% typesetting comment
	\label{lastpage}
\end{document}

>>>>

	In order to answer these questions it is necessary to identify a large sample of r-process stars.
	However, r-process stars are very rare. For this reason we must look to massive data sets, such as the LAMOST sky survey. In this letter we report the discovery of 47 r-process enhanced stars identified from LAMOST, significantly building upon the previously known Milky Way sample of 38 \citep[e.g.,][]{masho2011,Honda2004,Hayek2009,Sneden2003,Ivans2006,Hill2002,Christlieb2004,Wako2010,placo2017,Sakari2018,Hansen2018}.
	In Section 2 we outline the methods used to identify r-process enhanced candidates, and our analysis methods. In Section 3 we discuss what our results imply about the sites of the r-process. We provide concluding remarks in Section 4.

@@

	\subsection{Neutron-star mergers}
	\label{NSmerg}
	Neutron-star mergers are another possible site of r-process element nucleosynthesis \citep{Kasen2017,Hotok2013,Drout2017}. They satisfy the conditions necessary to create a high neutron density by means of interacting tidal forces between the stars, neutron dense material is accreted off the stars, allowing r-process element synthesis to occur. This specific process produces considerably more enriched material than core-collapse supernovae ($M_{\rm{Eu}}\approx10^{-4.5} M_{\odot}$) \citep{Goriely2011}, consistent with observed ejecta \citep{Kasliwal2017}. However, the direct interaction and merger of a binary neutron-star pair occurs very infrequently, with currently only one direct observation, and with a most plausible frequency estimate of 1,000$\,\rm{Gpc^{-3}yr^{-1}}$ \citep{LIGO2016,Abadie2010} well within the the outer estimates of $320\ \rm and 4780\ \rm{Gpc^{-3}yr^{-1}}$. The significant amount of material that these mergers release can compensate for their low frequency and so it could be that they are responsible for most if not all r-process enhancements observed.

@@

    It was found that in the Milky Way there should be present 13,060 r-process stars enhanced solely from neutron-star mergers. Taking into account that this should be considered a upper-bound estimate this is still a startlingly large difference from the known 85 r-process stars in the Milky Way.

    In preparing these calculations we assumed a constant star formation rate of 2 M$_\odot {\rm yr}^{-1}$ in the disk of the Milky Way, with a typical IMF and giant star birth rate of approximately 0.3 stars per year. Therefore if we assume a steady-state system, the number of red giant stars in the Milky Way comes to approximately $7.53\times10^7$. This allows us to find the fraction of the Milky Ways giants that our sample of r-process stars represents. Multiplying this fraction by the 13,060 stars that should be present in the Milky Way, we expect to be present 79 enhanced stars in LAMOST DR2, a number consistent with the 85 we now know of.

    For clarity we have also included the amount of stars expected should the rate of neutron star mergers be $320\ \rm{Gpc^{-3}yr^{-1}}$, in which case we expect there to be 4179 in Milky Way and 25 in LAMOST DR2. As well as what we expect should the rate be $4780\ \rm{Gpc^{-3}yr^{-1}}$, in which case in the Milky Way there would be 62426 and 377 expected in LAMOST DR2.

    Should we use another more realistic estimation supplied by Galaxia \todo{CITATION NEEDED}, where we have a total amount of giants in the disk and the bulge to be $4.8\times10^8$, we then expect to find 12 stars enhanced in LAMOST DR2. A less consistent number from what we have observed, but still comparable in orders of magnitude.

@@

    Following from the calculations above, neutron-star mergers could create enough r-process material to enrich above the point of [Eu/Fe] > 0.7 for the 47 known r-process enhanced stars within the LAMOST sample within $10.9\times10^{9}$ years, very close to the age of the universe as described in the calculation below:

    \begin{equation}
    	\rm Time = \frac{\rho_{\rm Eu}}{M_{\rm Eu,\ Ejecta}*Rate_{\rm NS\ star\ merger}}
    \end{equation}

	From our rates of core-collapse supernovae however, we find that the earliest time-scale at which they can create this level of r-process material is $2.4\times10^{11}$ years, orders of magnitude longer than the age of the universe. This illustrates, with our current knowledge of core-collapse supernovae frequency, and the amount of r-process material they eject, that core-collapse supernovae cannot be the sole source of r-process enrichment in the Milky Way.

@@

		\bibitem[\protect\citeauthoryear{Hansen et al.}{2018}]{Hansen2018}
		Hansen T. T., Holmbeck E. M., Beers T. C., Placco V. M., Roederer I. U., Frebel A., Sakari C. M., Simon J. D.,\& Thompson I. B. 2018, The Astrophysical Journal

@@

	% Don't change these lines
	\bsp	% typesetting comment
	\label{lastpage}
\end{document}
